---
title: "Visualizing prediction hubs in Chr12 from A549 Cell-line (GREG)"
author: "Shaurya Jauhari"
date: "8/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploring the prediction-hubs from A549 cell-line.

We attempt to map the prediction results corresponding to LR-Hubs from the A549 cell-line. It will be interesting to see the intersect of the pre-caliberated LR-Hubs and the ones predicted by the classifier.

The workflow commences with the installation of "Gviz" - the package we aim to deploy for the visualization.


```{r Installing package}

BiocManager::install("Gviz")
library(Gviz)
```

Next, we load the data from the A549 cell-line (GREG). This is a comprehensive data (genome-wide) with values corresponding to epigenetic marks (features) for each bin (a 2Kb genomic region), in addition to a "Class", i.e. a "Hub" or a "Non-Hub". For the present case, we shall prune the data for the genomic intervals and their corresponding class. That is all we need!

```{r loading data, echo=FALSE}

a549greg <- read.table("A549forML.txt", header = TRUE) ## full data
a549greg <- a549greg[, c(1:3,16)] ## genomic ranges and their class labels

```

Also, considering the computational resources we deploy, we shall focus on chromosome 21 only.


```{r extracting chr21 data}

a549gregChr21 <- a549greg[a549greg$chr=="chr21", ] ## subset of data for exemplifying
```

## Plotting Data

```{r}
annotationTrackChr21 <- AnnotationTrack(a549gregChr21[,1:3])
plotTracks(annotationTrackChr21)
```


